Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-03 article.tex
bookmark

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field, 
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
and the corresponding MC photograph \cref{fig:simulation_particles}(d)). 
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering and MC forward models. 
    (a) cross sections of the low density scene (\cref{fig:simulation-results1}(d)
    and \cref{fig:simulation_particles}(a)). (b) cross sections of
    the high density scene (\cref{fig:simulation_particles}(d)).
  }
  \label{fig:cross_sections}
\end{figure}

@@

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    single-scattering simulated images are used as input to the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}.
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[htbp]
  \centering
  \begin{tabular}{cccccg}
    \toprule
    Scene  & Forward & Aerosol & Isotropic     & Absorbing & $\epsilon$ \\
           & model&   density & Phase function? & aerosol?   & \\
     \midrule
    Haze Front & Single scatter & Low & & & 0.18 \\
          & Monte Carlo & Low & & & 0.65 \\
    \cmidrule(r){1-5}
    Haze Blobs & Single scatter & Low & & & 0.14 \\
     & Monte Carlo & Low & & & 0.65 \\
     & Monte Carlo & Low & $\surd$  & & 0.49 \\
     & Monte Carlo & Low & & $\surd$ & 0.83 \\
     & Monte Carlo & High & & & 0.98 \\
    \bottomrule
  \end{tabular}
  \caption{Relative error measure in various simulations}
  \label{tbl:mass}
\end{table}
The overall mass is recovered, but for 6.5\% loss. \\

>>>>

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field, 
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
and the corresponding MC photograph \cref{fig:simulation_particles}(d)). 
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering and MC forward models. 
    (a) cross sections of the {\em Haze Blobs} scene (\cref{fig:simulation-results1}(d)
    and \cref{fig:simulation_particles}(a)). (b) cross sections of
    the increased aerosol density scene (\cref{fig:simulation_particles}(d)).
  }
  \label{fig:cross_sections}
\end{figure}

@@

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    single-scattering simulated images are used as input to the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[htbp]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Scene      & Forward        & Aerosol density & Isotropic       & Absorbing & $\epsilon$ & Mass \\
               & model          & order           & Phase function? & aerosol?  &            & diff. \\
     \midrule
    Haze Front & Single scatter & $10^{6}$         &                 &           & 0.18       & 1.1\%  \\
               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 14\%  \\
    \cmidrule(r){1-5}
    Haze Blobs & Single scatter & $10^{6}$         &                 &           & 0.14       & 0\%  \\
               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 6.7\%  \\
               & Monte Carlo    & $10^{6}$         & $\surd$         &           & 0.49       & 2\%  \\
               & Monte Carlo    & $10^{6}$         &                 & $\surd$   & 0.83       & 9.6\%  \\
               & Monte Carlo    & $10^{7}$         &                 &           & 0.98       & 23\%  \\
    \bottomrule
  \end{tabular}
  \caption{Relative error measure in various simulations}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\
